A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling. He found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other. \citet{Renard_1997} then recommended that it is better to select a technique which provides block permeabilities instead of one which provides uniform effective permeability.

>>>>

\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling. They found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other. \citet{Renard_1997} then recommended that it is better to select a technique which provides block permeabilities instead of one which provides uniform effective permeability.
